Mergeable Types for Highly-Available Replicated Data

### 2017-02-23 paper/semantics.tex
Edits.

We will not present a series of definitions and results that let us
understand the premises of the \rulelabel{E-Pull-Wait} rule, examine
the merge operation in closer detail, and appreciate the need for
constraining the branching structure. First, we formalize the
intuitive notation of the ancestor relationship between versions of a
legal branching history (i.e., a branching history generated by the
rules in Fig.~\ref{fig:opsem}):

>>>>

We will now present a series of definitions and results that let us
understand the premises of the \rulelabel{E-Pull-Wait} rule, examine
the merge operation in closer detail, and appreciate the need for
constraining the branching structure. First, we formalize the
intuitive notation of the ancestor relationship between versions of a
legal branching history (i.e., a branching history generated by the
rules in Fig.~\ref{fig:opsem}):
